---
title: "Naive Bayes Classifier"
author: "Timothy Dunbar"
date: "June 12, 2017"
output:
  html_notebook: default
  html_document: default
---

### Naive Bayes Classifier *Refactor*

As the title suggests this post will be a refactoring of the code from the previous post.  I'm doing this partly because I recently watched all the videos from Robert Martin's (Uncle Bob's) Clean Code series but also because I think refactoring code is a good way to learn about it.

I might try to make refactoring code a regular part of this blog.

#### First a Recap

Here is the textCleaner function
```{r textCleaner, echo=TRUE}
textCleaner<-function(x){
  x<-scan(x, what="", sep="\n")
  #removes the author of the quote because I am only interested in male or female
  x<-gsub("--\\s.*", "", x)
  #removes punctiation
  x<-gsub("([-'])|[[:punct:]]", "", x)
  #splits on spaces
  x<-strsplit(x, "[[:space:]]+")
  #formats as data frame
  x<-as.data.frame(unlist(x))
  return(x)
}
```
And here is the Classifier code
```{r bayesClassifier, echo=TRUE}
bayesClassifier<-function(menClass, womenClass, document, menPrior, womenPrior){
  #gets counts of words in each class
  mCount<-nrow(menClass)
  wCount<-nrow(womenClass)
  #combines the menClass and womenClass dataframes into a vocabulary dataframe
  vocabAll<-rbind(menClass, womenClass)
  #collapses like words in vocabAll and find count of all unique words in vacabulary
  vocabAll<-as.data.frame(table(vocabAll))
  vocabCount<-nrow(vocabAll)
  #collapses menClass and womenClass data frames and finds the frequency of each word
  menClass<-as.data.frame(table(menClass))
  womenClass<-as.data.frame(table(womenClass))
  #finds intersection of document data frame and the menClass and womenClass dataframes
  intersectM<-menClass[is.element(menClass$menClass, intersect(document$`unlist(x)`, menClass$menClass)),]
  intersectW<-womenClass[is.element(womenClass$womenClass, intersect(document$`unlist(x)`, womenClass$womenClass)),]
  #conditional probabilities of each intersecting word, this would be the place to add smoothing if desired in place of the 0s
  intersectM$Freq<-(intersectM$Freq+0)/(mCount+vocabCount+0)
  intersectW$Freq<-(intersectW$Freq+0)/(wCount+vocabCount+0)
  #finds product the frequency column and multiplies by the priors
  posteriorM<-prod(intersectM$Freq)*menPrior
  posteriorW<-prod(intersectW$Freq)*womenPrior
  #test for higher posterior
  if(posteriorW>posteriorM){
    return("Female")
  }
  return("Male")
}
```
I will tackle the textCleaner part first.  My goal will be to make the code read like "well written prose" to quote Uncle Bob.  What this means is that all the comments I have in the code are only necessary because I did a terrible job writing the code in the first place.

First, I must write a test that the current code passes so that I know I didn't break anything while refactoring.  For that we are going to need the *testthat* library.
```{r necessary_packages, echo=TRUE}
install.packages('testthat')
library(testthat)
```
We also need a data frame made from the original function to test the new function against.  I've assigned it to a variable for simplicities sake.
```{r}
cleaned_test_file<-textCleaner('~/naive-bayes-classifier/refactor_test_file.txt')
```
And here is the unit test.
```{r}
test_that('textCleaner cleans', {
  test_file<-'~/naive-bayes-classifier/refactor_test_file.txt'
  
  expect_that(textCleaner(test_file), equals(cleaned_test_file))
})
```
I ran the unit test against the original function to prove the unit test itself works.  The lack of an error means that I am ready to refactor.

### Refactored textCleaner function
```{r text_cleaner_refactored, echo=TRUE}

# Here, I've broken out each of the seperate operations of the original code into their own function.
remove_author<-function(file){
  regex_author_pattern<-"--\\s.*"
  cleaned_file<-base::gsub(regex_author_pattern, "", file)
  return(cleaned_file)
}

remove_punctuation<-function(file){
  regex_punctuation_pattern<-"([-'])|[[:punct:]]"
  cleaned_file<-base::gsub(regex_punctuation_pattern, "", file)
  return(cleaned_file)
}

split_file<-function(file){
  regex_split_pattern<-"[[:space:]]+"
  cleaned_file<-base::strsplit(file, regex_split_pattern)
  return(cleaned_file)
}

clean<-function(file){
  cleaned_file<-remove_author(file)
  cleaned_file<-remove_punctuation(cleaned_file)
  cleaned_file<-split_file(cleaned_file)
  return(cleaned_file)
}

# An argument could be made that I didn't have to break out all the cleaning steps to their own clean function but I decided to go all out
clean_text_file_and_return_data_frame<-function(file){
  
  file<-base::scan(file, what="", sep="\n")
  
  cleaned_file<-clean(file)
  # annoyingly to get the test to pass I had to rename cleaned_file to x
  x<-cleaned_file
  x<-base::as.data.frame(unlist(x))
    
  return(x)
}
```
Now to use the test I wrote (and proved) earlier on the newly written function.
```{r}
test_that('textCleaner cleans', {
  test_file<-'~/naive-bayes-classifier/refactor_test_file.txt'
  
  expect_that(clean_text_file_and_return_data_frame(test_file), equals(cleaned_test_file))
})
```
Again, the lack of an error means that everything works.  Let's review:

* I used the original code to get a data frame into a variable
* I wrote a unit test against the original code
* I tested my unit test against the data frame variable produced by the original code
* Finally, I wrote and tested the new code.

The circle is now complete.

As noted in the comment in the above *clean_text_file_and_return_data_frame* function, to get the test to pass I had to rename my cleaned_file variable to x before I converted to a data frame and called the unlist function.

I have remedied that situation below.
```{r clean_text_file_and_return_data_frame fixed, echo=TRUE}
 clean_text_file_and_return_data_frame<-function(file){
  
  file<-base::scan(file, what="", sep="\n")
  cleaned_file<-clean(file)
    
  return(cleaned_file)
}
```
This code is much more readable and follows the single responsibility principle.  Now we need a whole new set of unit tests.

I'm not going to write a test for clean function because it's only responsiblity is to call the seperate functions that do the cleaning.

#### Unit test

First initialize the variables we will test against
```{r}

```

